---
title: "Week 2---Assignment"
output: html_notebook
---

# Recreate a graphic based on the readings from Chapter 3

This asignment asked you to reproduce one of the plots from the *Exercies 3.6.1* in **R for Data Science** 

Each of these charts is shown below. There may be other ways to recreate the graphics. 

## Required Packages
```{r Required Packages, echo=TRUE}
library(tidyverse)
```


## Graph 1---Top Left

Starting with the top left graphic:

```{r Graph1a-Top Left}
ggplot(data = mpg) +
  geom_point(mapping = aes(x= displ, y = hwy), size = 4) +
  geom_smooth(mapping = aes(x= displ, y = hwy), size = 2, se = FALSE)
```

The main changes in this graphic are the changes to the default size of the datapoints and the width of the line. 

I can reduce the amount of typing by including the file information in the ggplot() function.

```{r Graph 1b-Top Left}
# This can be simplified by mapping the aestheitcs in the ggplot()

ggplot(data = mpg, mapping = aes(x= displ, y = hwy)) +
  geom_point(size = 4) +
  geom_smooth(size = 2, se = FALSE)
```

***

## Graph 2---Top Right

The second graph shows the a regresion of the data by some factor (three of them)
Drivetrain (drv) was used earlier in the document and matches the desired output.

```{r Graph 2-Top Right}
ggplot(data = mpg, mapping = aes(x= displ, y = hwy)) +
  geom_point(size = 4) +
  geom_smooth(mapping = aes(group = drv), size = 2, se = FALSE)
```

***
## Graph 3---Middle Left

The middle left plot adds color to All the data colored by drivetrain:

```{r Graph3--Middle Left}
ggplot(data = mpg, mapping = aes(x= displ, y = hwy, colour = drv)) +
  geom_point(size = 4) +
  geom_smooth(mapping = aes(group = drv), size = 2, se = FALSE)
```

***

## Grah 4---Middle Right

If I want to only color the data points, I need to move the aes() back to the gopm_point() and geom_smooth() positions.

```{r Graph4-Middle Right}
ggplot(data = mpg) +
  geom_point(mapping = aes(x= displ, y = hwy, colour = drv), size = 4) +
  geom_smooth(mapping = aes(x= displ, y = hwy), size = 2, se = FALSE)
```

***
## Graph 5---Bottom Left

The bottom left requires we assign a *linetype* to each of the groups.

```{r Graph5-Bottom Left}
ggplot(data = mpg) +
  geom_point(mapping = aes(x= displ, y = hwy, colour = drv), size = 4) +
  geom_smooth(mapping = aes(x= displ, y = hwy, linetype = drv), size = 2, se = FALSE)
```

***
## Graph 6---Bottom Right

I constructed the final graph by layering two sets of points using geom_point(). It looks to be plotting the colored points over a larger white point.

```{r Graph6-Bottom Right}
ggplot(data = mpg) +
  geom_point(mapping = aes(x = displ, y = hwy), colour = "white", size = 8) +
  geom_point(mapping = aes(x = displ, y = hwy, colour = drv), size = 4)
```

